Scattering and Pair Processes in General Relativistic Ray Tracing for Neutrinos

### 2016-10-16 paper.tex
Flesh out Rendering Equation and adjust table positioning

\subsection{The Rendering Equation}
\label{ssec:rendering_eqn}
\todo{type up derivation from notes}
We can integrate Eqn.~\ref{eqn:boltzmann_linear} directly,
\begin{equation}
  \label{eqn:rendering}
  f(\lambda) = f(\lambda_e) e^{-\tau(\lambda,\lambda_e)} +
  \int_{\lambda_e}^\lambda d\lambda'\,e^{-\tau(\lambda,\lambda')}
  \mathscr{K}^*(\lambda') \mathscr{S}^*(\lambda'),
\end{equation}
where the parameterization conventions are depicted in
Fig.~\ref{fig:affine_param}.

\subsection{Neutrinosurface Approximation}
\label{ssec:neutrinosurface}
\todo{derive $\tau=2/3$ approx \cite[Chap.~4]{shu1991-book_radiation},
  and \cite{miln1921-radiative_equil_1}}
In the simplified configuration of a plane-parallel atmosphere, the
rendering equation reduces to 
\begin{equation}
\label{eqn:neutrinosurface}
  f(\lambda) = f^{\rm eq}(\lambda_e),
\end{equation}
where $\tau(\lambda,\lambda_e)=2/3$.

@@

\begin{table}
  \centering
  \begin{tabularx}{\columnwidth}{X X}
    \hline \hline
    absorption/emission
    & $\nu_e + n \leftrightarrow e^- + p$                          \\
    & $\bar{\nu}_e + p \leftrightarrow e^+ + n$                    \\
    & $\nu_e + {}^AZ \leftrightarrow e^- + {}^A(Z+1)$              \\
    & $\bar{\nu}_e + {}^AZ \leftrightarrow e^+ + {}^A(Z-1)$        \\
    \hline
    elastic scattering
    & $\nu + N \leftrightarrow \nu + N$                            \\
    & $\nu + {}^AZ \leftrightarrow \nu + {}^AZ$                    \\
    \hline
    inelastic scattering
    & $\nu + e^- \leftrightarrow \nu' + e^{-'}$                    \\
    & $\nu + e^+ \leftrightarrow \nu' + e^{+'}$                    \\
    \hline
    pair processes
    & $\nu + \bar{\nu} \leftrightarrow e^{-} + e^{+}$              \\
    & $\nu + \bar{\nu} + N + N \leftrightarrow N' + N'$            \\
    & $\nu + \bar{\nu} \leftrightarrow \gamma$                     \\
    \hline \hline
  \end{tabularx}
  \caption{
    We analyze neutrino interaction processes in terms of these categories.
    $\nu$ without a label represents a neutrino or antineutrino of any flavor,
    $N$ represents a nucleon $n$ or $p$,
    ${}^ZA$ represents a nucleus with mass number $A$ and charge $Z$, and
    $\gamma$ represents a high-energy photon.
    A prime indicates a change in that particle's energy.
  }
  \label{tab:neutrino_processes}
\end{table}

>>>>

\subsection{The Rendering Equation}
\label{ssec:rendering_eqn}
Defining the source function
$\mathscr{S}^*\equiv\mathscr{E}^*/\mathscr{K}^*$,
we can integrate Eqn.~\ref{eqn:boltzmann_linear} directly,
\begin{equation}
  \label{eqn:rendering}
  f(\lambda) = f(\lambda_e) e^{-\tau(\lambda,\lambda_e)} +
  \int_{\lambda_e}^\lambda d\lambda'\,e^{-\tau(\lambda,\lambda')}
  \mathscr{K}^*(\lambda') \mathscr{S}^*(\lambda'),
\end{equation}
where the optical depth is defined,
\begin{equation}
  \label{eqn:optical_depth}
  \tau(\lambda,\lambda') \equiv -\int_{\lambda'}^\lambda
  d\lambda'' \, \mathscr{K}^*(\lambda''),
\end{equation}
and the parameterization conventions are depicted in
Fig.~\ref{fig:affine_param}.

\subsection{Neutrinosurface Approximation}
\label{ssec:neutrinosurface}
\todo{derive $\tau=2/3$ approx \cite[Chap.~4]{shu1991-book_radiation},
  and \cite{miln1921-radiative_equil_1}}
In the simplified configuration of a plane-parallel atmosphere, the
rendering equation reduces to 
\begin{equation}
\label{eqn:neutrinosurface}
  f(\lambda) = f^{\rm eq}(\lambda_e),
\end{equation}
where $\tau(\lambda,\lambda_e)=2/3$.
At an optical depth of $2/3$, the energy flux is equivalent to the
the blackbody value $\sigma T^4$, with $\sigma$, the Stefan-Boltzmann radiation
constant.
\todo{verify}

@@

\begin{table}[h]
  \caption{
    We analyze neutrino interaction processes in terms of these categories.
    $\nu$ without a label represents a neutrino or antineutrino of any flavor,
    $N$ represents a nucleon $n$ or $p$,
    ${}^ZA$ represents a nucleus with mass number $A$ and charge $Z$, and
    $\gamma$ represents a high-energy photon.
    A prime indicates a change in that particle's energy.
  }
  \label{tab:neutrino_processes}
  \begin{tabularx}{\columnwidth}{X X}
    \hline \hline
    absorption/emission
    & $\nu_e + n \leftrightarrow e^- + p$                          \\
    & $\bar{\nu}_e + p \leftrightarrow e^+ + n$                    \\
    & $\nu_e + {}^AZ \leftrightarrow e^- + {}^A(Z+1)$              \\
    & $\bar{\nu}_e + {}^AZ \leftrightarrow e^+ + {}^A(Z-1)$        \\
    \hline
    elastic scattering
    & $\nu + N \leftrightarrow \nu + N$                            \\
    & $\nu + {}^AZ \leftrightarrow \nu + {}^AZ$                    \\
    \hline
    inelastic scattering
    & $\nu + e^- \leftrightarrow \nu' + e^{-'}$                    \\
    & $\nu + e^+ \leftrightarrow \nu' + e^{+'}$                    \\
    \hline
    pair processes
    & $\nu + \bar{\nu} \leftrightarrow e^{-} + e^{+}$              \\
    & $\nu + \bar{\nu} + N + N \leftrightarrow N' + N'$            \\
    & $\nu + \bar{\nu} \leftrightarrow \gamma$                     \\
    \hline \hline
  \end{tabularx}
\end{table}
